---
title: "Pets: Get started!"
author: "Klara Dolos"
date: "September 21, 2017"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{get_started}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Install the package
The package code can be found on github at the account of the Institute of Geography and Geoecology (KIT): https://github.com/KIT-IfGG

## Install from github

The easiest way to download and install an R-package that is hosted on Github is to use the function install_git of the package devtools.
1. Install devtools, if not done yet
2. Get link to the repository (green button on the github page)
3. Use function install_git with the right url

This works for all R-packages hosted in public repositories on Github!


```{r install_github, echo=TRUE}
# install.packages("devtools")
library(devtools)
install_github("KIT-IfGG/pets", auth_token = "258efa53825dac39ad132491a9900dcbfa74cd71",  build_vignettes = TRUE)

```

## Clone and build
You can clone the respository (e.g. using RStudio/projects/from version control...) and built the package yourself. This makes sense if you like to change code or add functions to the R-package and fix bugs. There are plenty of tutorials how to work with version control and especially git/RStudio.

# Report issues
 Certainly there will be issues and questions in using the package functions. You can use the issues tool of the Github repository to get answers and solutions.
 