---
title: "Neutral community model (NCM)"
author: "Klara Dolos"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{NCM}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

# Model description
## The system

## States
the number of beetles is recorded. Each time step a new set of states is created.

## Processes

The system is reduced to the following processes...


# Run the model

To run the model some function arguments need to be specified. 

```{r Simulate, eval=TRUE, echo=TRUE, include=TRUE, results='hide', fig.keep='last', fig.show='asis', strip.white=TRUE, fig.align='center', fig.width=7, fig.height=4}
library(pets)
neutral_community_model(nspecies=8, gridsize=20, time=100, pdf=FALSE, plotpop=TRUE, sleep=0)

```
Figure 1: Simulation of population dynamics.


```{r Simulate2, eval=TRUE, echo=TRUE, include=TRUE, results='hide', fig.keep='last', fig.show='asis', strip.white=TRUE, fig.align='center', fig.width=7, fig.height=4}

neutral_community_model_density(nspecies=8, gridsize=20, time=100)

```
Figure 2: Simulation of population dynamics with density dependend reproduction.

